---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rdtools

<!-- badges: start -->
<!-- badges: end -->

rdtools provides fast, cached lookup of help topics and aliases across
installed, source, and in-development packages, plus efficient retrieval of
parsed Rd objects. It's low-level infrastructure designed to be shared by
documentation tools like roxygen2, pkgdown, pkgload, and downlit, which
currently each implement their own variant of this machinery.

## Installation

You can install the development version of rdtools from
[GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("r-lib/rdtools")
```

## Usage

`pkg_topics()` maps every alias a package documents to the Rd file that
documents it:

```{r}
library(rdtools)

head(pkg_topics("stats"))
```

`topic_find()` tells you which package documents a topic, searching the
attached packages by default:

```{r}
topic_find("rnorm")

topic_parse("dplyr::across")
```

`topic_rd()` retrieves the parsed Rd for a topic, fetching it lazily from
the help database for installed packages, or parsing `man/*.Rd` for source
packages:

```{r}
rd <- topic_rd("rnorm", "stats")
class(rd)
```

All lookups are backed by per-package indexes that are cached and
automatically revalidated when the underlying files change, so they're
cheap enough to call in a tight loop (e.g. once per link while rendering
documentation).
